The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-08-10 manuscript/rebuttal.Rmd

Dear Editor,

Many thanks for your consideration of our manuscript.
Below is our point-by-point response to reviewer comments.

### Reviewer 1

> In this manuscript, the authors present a framework that computational researchers should follow to maximize the reproducibility of their computational research. The five pillars that they identified are 1) code version control and sharing, 2) compute environment control,  3) literate programming, 4) documentation and 5) FAIR data sharing. They give a fair amount of detail regarding each pillar. This paper contains no original research and is more of an opinion piece. With that in mind, if BiB is interested in this topic, I recommend publishing. The authors make very reasonable suggestions. My only request for edits is to rearrange the section structure of the manuscript to be in line with the numbering of the pillars. Right now it is quite confusing.

Response: We thank the reviewer for their positive feedback.
With regards to the ordering of the five pillars, we have altered Figure 1 so that the pillars now
appear in the same order as they are detailed in sections following.

### 2023-08-10 manuscript/5pillars.Rmd
#25 close. Have fixed figure 1 so the order of pillars is same as the text

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
author: "Mark Ziemann, Pierre Poulain, Anusuiya Bora"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: 5pillars.bib
csl: plos-computational-biology.csl
---

Mark Ziemann<sup>1*</sup>, Pierre Poulain<sup>2</sup>, Anusuiya Bora<sup>1</sup>

@@

labs <- c("Code version\ncontrol &\npersistent\n sharing",
  "Compute \nenvironment \ncontrol",
  "Literate\nprogramming",
  "Documentation",
  "FAIR &\npersistent\ndata sharing")

>>>>

---
title: "The five pillars of computational reproducibility: Bioinformatics and beyond"
date: "`r Sys.Date()`"
output:
  rmdformats::robobook:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 5
    fig_height: 5
bibliography: 5pillars.bib
csl: plos-computational-biology.csl
---

<strong>Mark Ziemann<sup>1*</sup>, Pierre Poulain<sup>2</sup>, Anusuiya Bora<sup>1</sup></strong>

@@

labs <- c("Literate\nprogramming",
  "Code version\ncontrol &\npersistent\n sharing",
  "Compute \nenvironment \ncontrol",
  "FAIR &\npersistent\ndata sharing",
  "Documentation")
